\LARGE \bf Mean Estimation from One-Bit Measurements

### 2020-12-20 proof-lan-distributed.tex
removed expressions with \pm

To see the first claim of the lemma, we consider the simpler special case
that $A = [a, b]$. Then as $f$ is Lipschitz (and hence absolutely
continuous and a.e.\ differentiable with $\linf{f'} \le \lip(f)$),
we have
\begin{align*}
  P_{\theta + h}(A)
  - P_\theta(A)
  & = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
  & = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
  & = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
  & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
  & = \int_0^h (f(a - \theta) - f(b - \theta)) du
  \pm 2 \int_0^h \lip(f) u du \\
  & = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
\end{align*}
This gives the first two claims of the lemma.

@@

Now, we write the log-likelihood ratio. We have
\begin{align*}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  & = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
  & = \sum_{i = 1}^n W_{n,i}
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2
  + \half \sum_{i = 1}^n W_{n,i}^2 R(W_{n,i})
\end{align*}
where the remainder $|R(W_{n,i})| \le |W_{n,i}|$ for $|W_{n,i}| \le 1$.
Using the Taylor expansions of $\sqrt{\cdot}$ and
Lemma~\ref{lemma:derivative-bounds}, we have
\begin{align}
  \nonumber
  \half W_{n,i}
  & = \half \score_\theta(B_i)
  \frac{h_n}{\sqrt{n}}
  \pm \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
  + \frac{h_n^2}{n} \score_\theta(B_i)^2
  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \\
  & = \half \score_\theta(B_i)
  \frac{h_n}{\sqrt{n}} +
  C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right|
  \label{eqn:max-wni-zero}
\end{align}
where $|C| < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
uniformly bounded. From Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} we get
\[
C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right| \to 0. 
\]
Consequently $\max_i W_{n,i} \to 0$, so that
\begin{equation}
  \label{eqn:almost-at-the-end}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  = \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
\end{equation}

>>>>

To see the first claim of the lemma, we consider the simpler special case
that $A = [a, b]$. Then as $f$ is Lipschitz (and hence absolutely
continuous and a.e.\ differentiable with $\linf{f'} \le \lip(f)$),
we have
\begin{align*}
  P_{\theta + h}(A)
  - P_\theta(A)
  & = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
  & = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
  & = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
  & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
  & \lesseqgtr \int_0^h (f(a - \theta) - f(b - \theta)) du
  \pm 2 \int_0^h \lip(f) u du \\
  & = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
\end{align*}
This gives the first two claims of the lemma.

@@

Now, we write the log-likelihood ratio. We have
\begin{align*}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  & = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
  & = \sum_{i = 1}^n W_{n,i}
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2
  + \half \sum_{i = 1}^n W_{n,i}^2 R(W_{n,i})
\end{align*}
where the remainder $|R(W_{n,i})| \le |W_{n,i}|$ for $|W_{n,i}| \le 1$.
Using the Taylor expansions of $\sqrt{\cdot}$ and
Lemma~\ref{lemma:derivative-bounds}, we have
\begin{align}
  \nonumber
  \left| \half W_{n,i} \right|
  & \leq \half \left| \score_\theta(B_i) \right|
  \frac{h_n}{\sqrt{n}}
  + \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
  + \frac{h_n^2}{n} \score_\theta(B_i)^2
  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \\
  & = \half \score_\theta(B_i)
  \frac{h_n}{\sqrt{n}} +
  C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right|
  \label{eqn:max-wni-zero}
\end{align}
where $|C| < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
uniformly bounded. From Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} we get
\[
C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
  + \frac{k_i}{n p(B_i)}
  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
  + \frac{k_i^2}{p(B_i)^2 n^2}
  \right| \to 0. 
\]
Consequently $\max_i W_{n,i} \to 0$, so that
\begin{equation}
  \label{eqn:almost-at-the-end}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  = \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
\end{equation}
